Automated verification of stand-alone solar photovoltaic systems

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed sections 3 and 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

PV systems are broadly classified into three distinct types \cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, (2) grid-connected systems, and (3) solar PV hybrid system. %, where another source(s) of energy can work together with the solar PV. % system to provide the required demand.
%, such as wind, biomass or diesel, 
%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
%
%\begin{itemize}
%\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants; 
%\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
%\end{itemize}
Specifically concerning the energy need for remote rural areas of developing countries or places where the grid extension is not possible or feasible, 
%stand-alone systems are one the most used solutions, and 
% depending on the type of load, cost, resources availability, and requirements of the load, 
%stand-alone systems 
%can be split into several categories. However, 
the configuration that is most common or mode indicated is the regulated stand-alone system with battery and AC load. This configuration is the focus of this paper.
%, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
%PV array, battery, MPPT and AC load. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}. Because of the AC load, an inverter (DC to AC converter) is required. 
%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.

@@

\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
%
In order to address different aspects of project system and systems design, there is a myriad of tools. 
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
 to complex financial analysis and project optimization. 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
Here it was evaluated the most popular tools, as PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2.

@@

Table~\ref{table:softwares} summarizes the off-the-shelf tools employed in this study, where only Hybrid2 does not have technical support; HOMER Pro and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis; 
additionally, HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis. However, only paid version (restrict to the Microsoft Windows Operational System) of those tools have all the features, as to save the the project or to upload data from manufacturers. RETScreen and HOMER have a free web-based version, but they have limited resources.

@@

%-------------------------------------------------------------------
%\subsection{Paper Proposal x Reference Tools}
%-------------------------------------------------------------------
%
Considering the focus of this paper, only HOMER remains for a comparative with the proposed automated verification technique of this paper. %All tools need some parameters inherently from manufacturer's catalog.
%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
%After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
And the challenge of this work is to show that is possible to use automated verification in stand-alone PV solution, proving that this evaluation is more efficient and complete than other state-of-the-art tool, as HOMER Pro. The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section \ref{sec:results}.

@@

%The main purpose of this section is to describe the models for the elements of a stand-alone PV system: PV generator, battery, controller, inverter, and load. 
The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. It is identified the PV generator, batteries, charge controller, inverter, and AC load.

The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. At the diagram, there are two variables that depend on the site where the system is deployed and from the weather (solar irradiance $ G $ and temperature $ T $). For night hours or rainy days, one needs to hold batteries, where power can be stored and used. The use of battery as a storage form implies thus the presence of a charge controller \cite{Hansen}, \cite{Mellit}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called of inverter. And the AC load dictates the behavior of AC electrical load from the house that will be feed by the system.
%
%The modular structure facilitates the modeling of the other system structures and replacement of elements, such as a DC load instead of an AC load. 
%
\begin{figure}[h]
\includegraphics[width=0.48\textwidth]{blockdiagramPVS}
\centering
\caption{Block diagram for the stand-alone PV system (Source:~\cite{Hansen}).}
\label{fig:blockdiagram}
\end{figure}

@@

The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
is usually studied using an equivalent circuit model, as described in the available literature \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}. This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}. 
%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
\begin{figure}[h]
\includegraphics[width=0.20\textwidth]{equivckt1D}
\centering
\caption{1-diode equivalent PV cell/panel circuit model (Source:~\cite{Cubas}).}
%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
\label{fig:equivckt}
\end{figure}

The 1-diode model, shown by Fig. \ref{fig:equivckt}, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in (\ref{eq:1diodemodel}). 
\begin{equation}
\label{eq:1diodemodel}
I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right] 
\end{equation}

Where: $I_{ph}$ is the photocurrent delivered by the constant current source; $ I_{0} $ is the reverse saturation current corresponding to the diode; $ N $ is the number of series-connected cells ($ N=1 $ in a single cell configuration); $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $ T $ the temperature of the p-n junction (or cell temperature) in Kelvin; $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).

@@

%Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
The simplified model of 1-diode was shown that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested \cite{Saloux}. In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing.

%\subsection{PV Panel Model}
%With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
%
%A single-diode without series and shunt resistances is considered. 
Equation (\ref{eq:1diodemodel}) is used to write down expressions for currents and voltages at each key point of characteristic curve from a PV cell.
% shown in Fig. \ref{fig:ivcurve}.
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{ivcurve}
%\centering
%\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
%\label{fig:ivcurve}
%\end{figure}

@@

The voltage and the current at the maximum power point tracking (MPPT), can be expressed by (\ref{eq:Vmfinal}), (\ref{eq:Imfinal}), and (\ref{eq:Pm}) \cite{Saloux}. %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
\begin{equation}
\label{eq:Vmfinal}
V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) 
\end{equation}

@@

%\begin{multline}
%\label{eq:Pm}
%P_{m} = V_{m} I_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \\ \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right] 
%\end{multline}
%
However, the photocurrent delivered by the constant current source ($ I_{ph} $) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers. Therefore, (\ref{eq:Iph}) is used to calculate the photocurrent as function of irradiance and temperature \cite{Villalva}.
\begin{equation}
\label{eq:Iph}
I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right] 
\end{equation}

Where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions 
(provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).

The cell temperature ($ T $) is shown in (\ref{eq:Tcell}) \cite{Ross}.
\begin{equation}
\label{eq:Tcell}
T = T_{air} + \dfrac{NOCT-20}{800}G
\end{equation}

Where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is find at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.

Furthermore, (\ref{eq:I0}) allows the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature \cite{Villalva}. 
%In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).

\begin{equation}
\label{eq:I0}
I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1}
\end{equation}

Where $ V_{oc,ref} $ is the reference open-circuit voltage, and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).

%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
Using the maximum power point current (\ref{eq:Pm}) and the saturation current in the reference temperature given by (\ref{eq:I0}), the diode ideality factor is determined by (\ref{eq:a}).
\begin{equation}
\label{eq:a}
a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) }
\end{equation}

Where $ V_{mref} $, $ V_{oc,ref} $, $ I_{m,ref} $, and $ I_{sc,ref} $ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers. The model is now completely determined.
%; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
%
%If the PV cells are in parallel, then there is a parallel array. Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
%
%\begin{equation}
%\label{eq:Iarray}
%I_{array} = (N_{cells in parallel})(I_{one cell})
%\end{equation}
%
%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
%
%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
%
%\begin{equation}
%\label{eq:Varray}
%V_{array} = (N_{cells in series})(V_{one panel})
%\end{equation}
%
%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.

Besides the model verification, there is the prior stage of project sizing check, based on manufacturer's data and information from the sizing and the site.

First is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$). That is done by (\ref{eq:Ecorrected}) \cite{Pinho}. Where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }
\end{equation}

The total minimum number of solar panels necessary($ N_{TPmin} $) is calculated by  (\ref{eq:NTPmin}), and the check is done with (\ref{eq:NTP}), where the sized number of panels ($ N_{TP} $) must be greater than the result from (\ref{eq:NTPmin}).
\begin{equation}
\label{eq:NTPmin}
N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}
\end{equation}

\begin{equation}
\label{eq:NTP}
N_{TP} \geq N_{TPmin}
\end{equation}

Particularly, the total number of panels is series ($ N_{PSmin} $) and parallel ($ N_{PPmin} $) are given by (\ref{eq:NPSmin}) and (\ref{eq:NPPmin}), respectively. With the check done by (\ref{eq:NPS}) and (\ref{eq:NPP}). $ V_{system} $ is the DC voltage of the bus, normally 12, 24 or 48 V.
\begin{equation}
\label{eq:NPSmin}
N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}
\end{equation}

\begin{equation}
\label{eq:NPPmin}
N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}
\end{equation}

\begin{equation}
\label{eq:NPS}
N_{PS} \geq N_{PSmin}
\end{equation}

\begin{equation}
\label{eq:NPP}
N_{PP} \geq N_{PPmin}
\end{equation}

\subsection{The Battery Storage Model }
%Because of the fluctuating nature of the output delivered by the PV arrays, batteries are nece\sqrt{•}ry in a PV system. Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery. During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.

>>>>

PV systems are broadly classified into three distinct types~\cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system. %, where another source(s) of energy can work together with the solar PV. % system to provide the required demand.
%, such as wind, biomass or diesel, 
%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
%
%\begin{itemize}
%\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants; 
%\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
%\end{itemize}
Specifically concerning the energy needed for remote rural areas of developing countries or places where the grid extension is not possible or feasible, 
%stand-alone systems are one the most used solutions, and 
% depending on the type of load, cost, resources availability, and requirements of the load, 
%stand-alone systems 
%can be split into several categories. However, 
the configuration that is most common or more suitable is the regulated stand-alone system with battery and AC load. This configuration is the focus of this study.
%, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
%PV array, battery, MPPT and AC load. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}. Because of the AC load, an inverter (DC to AC converter) is required. 
%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.

@@

\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
%
In order to address different aspects of project system and systems design, there are various software tools \textcolor{red}{add citations here}. 
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
 to complex financial analysis and project optimization. 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
Here it was evaluated the most popular ones, which are PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2 \textcolor{red}{add citations here}.

@@

Table~\ref{table:softwares} summarizes the off-the-shelf tools employed in this study, where only Hybrid2 does not have technical support; HOMER Pro and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis; 
additionally, HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis. However, only commercial version (restricted to the Microsoft Windows OS) of those tools have all the features \textcolor{red}{these are really all features that are needed?}: to save the project or to upload data from manufacturers. RETScreen and HOMER have a free web-based version, but they have limited resources.

@@

%-------------------------------------------------------------------
%\subsection{Paper Proposal x Reference Tools}
%-------------------------------------------------------------------
%
Considering the focus of this study, only HOMER remains for a comparative evaluation with our proposed automated verification technique. %All tools need some parameters inherently from manufacturer's catalog.
%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
%After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
The main challenge of this study is to show that it is possible to use automated verification in stand-alone PV solution, thus proving that this evaluation is more efficient and complete than other state-of-the-art tool, as HOMER Pro. The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section~\ref{sec:results}.

@@

%The main purpose of this section is to describe the models for the elements of a stand-alone PV system: PV generator, battery, controller, inverter, and load. 
The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load.

The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. In the diagram, there are two variables that depend on the site where the system is deployed and from the weather (solar irradiance $G$ and temperature $T$). For night hours or rainy days, one needs to hold batteries, where power can be stored and used. The use of battery as a storage form implies thus the presence of a charge controller~\cite{Hansen,Mellit}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
%
%The modular structure facilitates the modeling of the other system structures and replacement of elements, such as a DC load instead of an AC load. 
%
\begin{figure}[h]
\includegraphics[width=0.48\textwidth]{blockdiagramPVS}
\centering
\caption{Block diagram for the stand-alone PV system (Source:~\cite{Hansen}).}
\label{fig:blockdiagram}
\end{figure}

@@

The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
is usually studied using an equivalent circuit model, as described in the available literature~\cite{Yatimi,Saloux,Mellit}. This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, in order to take into account energy losses in this model~\cite{Cubas}. 
%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
\begin{figure}[h]
\includegraphics[width=0.20\textwidth]{equivckt1D}
\centering
\caption{1-diode equivalent PV cell/panel circuit model (Source:~\cite{Cubas}).}
%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
\label{fig:equivckt}
\end{figure}

The 1-diode model, illustrated in Fig. \ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described in \eqref{eq:1diodemodel}. 
\begin{equation}
\label{eq:1diodemodel}
I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right], 
\end{equation}

\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells ($N=1$ in a single cell configuration); $a$ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $T$ the temperature of the p-n junction (or cell temperature) in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).

@@

%Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}. In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing.

%\subsection{PV Panel Model}
%With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
%
%A single-diode without series and shunt resistances is considered. 
Equation \eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \textcolor{red}{Add citation here}.
% shown in Fig. \ref{fig:ivcurve}.
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{ivcurve}
%\centering
%\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
%\label{fig:ivcurve}
%\end{figure}

@@

The voltage and the current at the maximum power point tracking (MPPT), can be expressed by \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm} \cite{Saloux}. %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
\begin{equation}
\label{eq:Vmfinal}
V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) 
\end{equation}

@@

%\begin{multline}
%\label{eq:Pm}
%P_{m} = V_{m} I_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \\ \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right] 
%\end{multline}
%
However, the photocurrent delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers. Therefore, (\ref{eq:Iph}) is used to calculate the photocurrent as function of irradiance and temperature~\cite{Villalva}.
\begin{equation}
\label{eq:Iph}
I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right], 
\end{equation}

\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions 
(provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).

The cell temperature ($ T $) is shown in (\ref{eq:Tcell}) \cite{Ross}.
\begin{equation}
\label{eq:Tcell}
T = T_{air} + \dfrac{NOCT-20}{800}G,
\end{equation}

\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet \textcolor{red}{add citation here}, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.

Furthermore, \eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature~\cite{Villalva}. 
%In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).

\begin{equation}
\label{eq:I0}
I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1},
\end{equation}

\noindent where $ V_{oc,ref} $ is the reference open-circuit voltage, and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).

%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
Using the maximum power point current (\ref{eq:Pm}) and the saturation current in the reference temperature given by (\ref{eq:I0}), the diode ideality factor is determined by (\ref{eq:a}).
\begin{equation}
\label{eq:a}
a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) },
\end{equation}

\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers; the model is now completely determined \textcolor{red}{which model? please be more specific}.
%; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
%
%If the PV cells are in parallel, then there is a parallel array. Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
%
%\begin{equation}
%\label{eq:Iarray}
%I_{array} = (N_{cells in parallel})(I_{one cell})
%\end{equation}
%
%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
%
%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
%
%\begin{equation}
%\label{eq:Varray}
%V_{array} = (N_{cells in series})(V_{one panel})
%\end{equation}
%
%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.

In addition to the model verification, there is the prior stage of project sizing check, based on manufacturer's data and information from the sizing and the site.

Firstly, it is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$). That is done by \eqref{eq:Ecorrected}~\cite{Pinho}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

The total minimum number of needed solar panels ($N_{TPmin}$) is computed by \eqref{eq:NTPmin}, and the check is performed using \eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from \eqref{eq:NTPmin}.
\begin{equation}
\label{eq:NTPmin}
N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
\end{equation}

\begin{equation}
\label{eq:NTP}
N_{TP} \geq N_{TPmin}.
\end{equation}

Particularly, the total number of panels is series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by \eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively. With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}). $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
\begin{equation}
\label{eq:NPSmin}
N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}.
\end{equation}

\begin{equation}
\label{eq:NPPmin}
N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}.
\end{equation}

\begin{equation}
\label{eq:NPS}
N_{PS} \geq N_{PSmin}.
\end{equation}

\begin{equation}
\label{eq:NPP}
N_{PP} \geq N_{PPmin}.
\end{equation}

%------------------------------------------------------------
\subsection{The Battery Storage Model }
%------------------------------------------------------------

%Because of the fluctuating nature of the output delivered by the PV arrays, batteries are nece\sqrt{•}ry in a PV system. Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery. During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.
